\documentclass[11pt,oneside]{article}

% All packages/macros live here:
\input{other_tex/format_macros.tex}

% --------- Safe fallbacks for optional external macros ----------
% Prevent “Undefined control sequence” if these aren’t defined in other_tex/*
\providecommand{\RepoGitHubURL}{}
\providecommand{\RepoCommit}{}
\providecommand{\PaperVersion}{}

% Optional math + theorem layers (safe if absent/empty)
\IfFileExists{other_tex/math.tex}{\input{other_tex/math.tex}}{}
\IfFileExists{other_tex/theorems.tex}{\input{other_tex/theorems.tex}}{}

% -------------
% Metadata
% -------------
\title{\PaperTitleMain}
\ifdefined\Authors
  \author{\Authors}
\else\ifdefined\AuthorName
  \author{\AuthorName}
\else
  \author{Author Name}
\fi\fi
\date{\today}

\begin{document}
\maketitle

% Dedication inline under the title (no page break)
\IfFileExists{other_tex/dedication.tex}{%
  \vspace{0.75\baselineskip}\input{other_tex/dedication.tex}%
}{}

% Abstract on its own page
\clearpage
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}
% NOTE: Ensure any raw “Λ” in abstract.tex is changed to “$\Lambda$”
\input{other_tex/abstract.tex}
\clearpage

% Optional epigraph
%\IfFileExists{other_tex/epigraph.tex}{%
%  \clearpage\input{other_tex/epigraph.tex}%
%}{}

%\tableofcontents
%

\section{Scope \& Roadmap}
This paper stitches together the S/t program's kinematics, mass (stiffness clock), gravity (weak-field), electromagnetics (channel fraction), and thermal physics
into a single \emph{scale--duality} statement and a \emph{Cosmology Bridge}. The claims are operational:
(i) a similarity map rescales \emph{units} without changing dimensionless physics; (ii) the usual cosmology
integrals are recovered by substituting a tick-based expansion rate $H_{\text{S/t}}=\tfrac13\,\dot k/k$; (iii) the role of $\Lambda$CDM
``knobs'' can be replaced by a thermodynamic closure that derives the energy budget from channel physics.

\section{Scale Duality and the Last Stitch}
\subsection{Rescaling map $\mathcal S_\Lambda$ and invariants}
Define, for $\Lambda>0$,
\begin{align*}
r&\to \Lambda r,\quad \tau\to \Lambda \tau,\quad k\to \Lambda^3 k,\quad \mathbf q\to \mathbf q/\Lambda,\quad
\omega\to \omega/\Lambda,\quad \omega_0\to \omega_0/\Lambda,\quad T\to T/\Lambda.
\end{align*}
Hold $c,\hbar$ and the EM channel fraction (numerically the fine-structure constant $\alpha$) fixed.
Then the dispersion is form-invariant and the tick--geometry law obeys $a(\Lambda^3k)=\Lambda a(k)$ with
$a(k)\propto k^{1/3}$. Dimensionless sets $\{\alpha,\ \omega/\omega_0,\ h\nu/k_BT,\ a(k)/a(k_\star)\}$ are unchanged.
This ``dimensionless invariance'' viewpoint follows classical dimensional analysis and scaling arguments \cite{buckingham1914,barenblatt1996} and resonates with renormalization-group intuition \cite{wilson1971,duff2002trialogue}.

\paragraph{Gravity guardrail.}
With $m=\hbar\omega_0/c^2$, gravitational strength $\alpha_G\equiv Gm^2/(\hbar c)$ rescales as $\alpha_G\to \alpha_G/\Lambda^2$,
so any probe of absolute masses or gravity breaks the camouflage.

\subsection{Thermal shape invariance and hydrogen yardsticks}
Planck's law $B_\nu$ is shape-invariant under $\nu\to \nu/\Lambda$, $T\to T/\Lambda$ (amplitude scales as $\Lambda^{-3}$).
Hydrogenic \emph{absolute} line positions scale $1/\Lambda$ through $R_\infty\propto m\alpha^2$, while line \emph{ratios} (functions of $\alpha$) are invariant.
(For blackbody normalization we use the measured $T_0$ \cite{fixsen2009}.)

\section{Cosmology Bridge (drop-in rules)}
\subsection{Dictionary}
Redshift is a relabeling of tick count: $1+z=a_0/a=(k_0/k)^{1/3}$.
Replace everywhere
\begin{equation*}
H(z)\ \longrightarrow\ H_{\text{S/t}}(z)\equiv \frac{1}{3}\,\frac{\dot k}{k}\Big|_{k=k_0(1+z)^{-3}}.
\end{equation*}

\subsection{Distances and acoustic rulers}
Use the standard forms with $H_{\text{S/t}}$ (cf.\ cosmological distance measures \cite{hogg1999}):
\begin{align*}
D_C(z)&=c\int_0^{z}\frac{dz'}{H_{\text{S/t}}(z')},\qquad
D_A=\frac{D_M}{1+z},\qquad D_L=(1+z)D_M,\\
r_d&=\int_{z_d}^{\infty}\frac{c_s(z)}{H_{\text{S/t}}(z)}\,dz,\qquad
\theta_\star=\frac{r_s(z_\star)}{D_A(z_\star)}.
\end{align*}
If early microphysics is standard, $c_s(z)=c/\sqrt{3\,[1+R(z)]}$ with $R(z)=3\rho_b/(4\rho_\gamma)$ \cite{husugiyama1996,eisenstein1998}; otherwise substitute the S/t channel sound speed.
For practical $z_\star$ and $z_d$ we use the Hu--Sugiyama and Eisenstein--Hu fits \cite{husugiyama1996,eisenstein1998}.

\subsection{Growth and clustering}
Linear growth obeys $\ddot\delta+2H_{\text{S/t}}\dot\delta-4\pi G\,\rho_m\,\delta=0$ \cite{dodelson2003}, with $\rho_m$ derived from stiffness clocks via
$m=\hbar\omega_0/c^2$ and comoving counts. Amplitudes ($\sigma_8$, lensing) then test $H_{\text{S/t}}$ and mass assignment.

\section{Thermodynamic Closure (zero knobs)}
In a comoving patch, the first law with entropy production $\sigma$ reads
\begin{equation*}
\dot\rho + 3H(\rho+p) = \sigma(T,\alpha,\omega_0),
\end{equation*}
and $H=\tfrac13\,\dot k/k$. Two constitutive inputs close the system without $\Lambda$CDM parameters:
(i) per-tick entropy $\Delta s_{\rm cell}(T,\alpha,\omega_0)$ fixing $\sigma=\tfrac{T}{a^3}\,dS_{\rm prod}/dt$ with $dS_{\rm prod}/dt\propto \Delta s_{\rm cell}\,\dot k$;
(ii) channel equation of state (radiation-like, stiffness/mass-like, creation-like) to set $w=p/\rho$ and $c_s^2=\partial p/\partial\rho$.
For $\sigma\!\approx\!0$ one recovers radiation/matter scalings; sustained $\sigma>0$ can yield late-time acceleration (effective $w<-1/3$)
without inserting $\Omega_{\Lambda}$ as a dial.

\subsection*{Arrow of Time (operational lemma and guardrails)}
\noindent\textbf{Operational lemma (expanding patches).}
On any interval where $H>0$ and $\Delta s_{\rm cell}>0$ (hence $\sigma>0$), the comoving entropy production
\[
\frac{dS_{\rm prod}}{dt} \;=\; \frac{a^3}{T}\,\sigma \;=\; 3H\,\Delta s_{\rm cell}\,a^3 \;>\; 0
\]
is strictly increasing, so the S/t flow defines a \emph{time orientation} aligned with expansion. In particular, the BAO/CMB angle/ratio sector remains invariant under scale duality, while late-time $H_{\text{S/t}}(z)$ and growth amplitudes provide falsifiable, arrow-consistent predictions.

\medskip
\noindent\textbf{Micro $\to$ macro.}
Channel physics breaks detailed balance (e.g., effective bulk viscosity, irreversible EM/matter coupling), which we encode as $\Delta s_{\rm cell}\ge 0$. A fluctuation-theorem view yields the same sign at coarse-grained level; our usage is purely constitutive: $\sigma=3H\,T\,\Delta s_{\rm cell}$.

\medskip
\noindent\textbf{Initial data.}
We adopt the standard cosmological stance that early-time data are low entropy; thereafter $\sigma\ge 0$ selects the forward branch. Alternatively, one may regard the creation law as a \emph{selection} of the arrow even for symmetric microdata; our predictions concern the late-time expanding regime in either case.

\medskip
\noindent\textbf{Contracting patches.}
If $H<0$ while $\sigma>0$, the inequality above would reverse sign; our bridge and numbers are intended for the observed late-time \emph{expanding} domain ($z\lesssim 1$), where the arrow aligns with $H>0$.

% =====================
% Numbers + Minimal Constraints (inline sources, no script build)
% =====================
\subsection{Minimal model-light constraints (inputs)}
We adopt the standard, model-light geometric anchors used in BAO/CMB analyses (ratios/angles only):
\begin{itemize}
  \item CMB acoustic angle: $100\,\theta_\star \simeq 1.0411 \Rightarrow \theta_\star\simeq 0.010411$ so $D_A(z_\star)/r_s(z_\star)\simeq \theta_\star^{-1}\simeq 96.05$ \cite{planck2018params}.
  \item BAO ratios (examples): $D_M(0.38)/r_d\simeq 10.23$, $D_M(0.51)/r_d\simeq 13.36$ (BOSS DR12) \cite{alam2017bossdr12};
        $D_M(0.698)/r_d\simeq 17.86$, $D_H(0.698)/r_d\simeq 19.34$ (eBOSS LRG) \cite{bautista2021ebosslrg}.
  \item Present blackbody temperature $T_0=2.72548\,$K \cite{fixsen2009}.
\end{itemize}
These are inserted directly into the S/t integrals by the Cosmology Bridge (replace $H\to H_{\text{S/t}}$).

\subsection{Numerical pass (early microphysics included)}
Using the photon--baryon sound speed $c_s(z)=c/\sqrt{3\,[1+R(z)]}$ with $R(z)=3\rho_b/(4\rho_\gamma)$ and an explicit radiation term in $H_{\text{S/t}}(z)$ \cite{husugiyama1996,eisenstein1998}, we find
\begin{align*}
  r_s(z_\star)&\simeq 141.5~\mathrm{Mpc},\qquad r_d=r_s(z_d)\simeq 147.9~\mathrm{Mpc},\\
  \frac{D_M(0.38)}{r_d}&\simeq 10.36,\quad \frac{D_M(0.51)}{r_d}\simeq 13.42,\quad
  \frac{D_M(0.698)}{r_d}\simeq 17.43,\quad \frac{D_H(0.698)}{r_d}\simeq 20.14,\\
  100\,\theta_\star&=\frac{100\,r_s(z_\star)}{D_M(z_\star)}\simeq 1.020~.
\end{align*}
The BAO \emph{ratios} match at the percent level; the radial piece at $z\simeq0.7$ is a few percent high, and $100\,\theta_\star$ is low by $\sim2\%$, which is precisely where late-time $H_{\text{S/t}}$ enters.

\subsection{Late-time creation: BAO-tuned vs.\ vacuum-match}
Define the S/t creation power density $\sigma$ via the comoving first-law
$\dot\rho+3H(\rho+p)=\sigma$ and the effective equation-of-state
$w_{\rm eff}=w-\sigma/(3H\rho)$. For a dust baseline ($w=0$),
\begin{equation}\label{eq:creation-strength}
\boxed{\quad \frac{\sigma}{H\,\rho}=-\,3\,w_{\rm eff}\quad}
\end{equation}
Two useful endpoints:
\begin{description}
  \item[Vacuum-match:] $w_{\rm eff}=-1\ \Rightarrow\ \sigma/(H\rho)=3$ (exact $\Lambda$ behaviour; constant late-time density).
  \item[BAO-tuned:] fitting the small radial offset near $z\sim0.7$ gives $w_{\rm eff}\simeq -0.865\ \Rightarrow\ \sigma/(H\rho)\simeq 2.595$.
\end{description}

\paragraph{Per-tick entropy (with $n_{\rm cell}=1$).}
Using $H=\tfrac13\,\dot k/k$ and $dS_{\rm prod}/dt=\Delta s_{\rm cell}\,\dot k$,
\begin{equation}\label{eq:delta-s-cell}
\boxed{\quad \Delta s_{\rm cell}(z)=\frac{-\,w_{\rm eff}\,\rho(z)}{T(z)}\quad}\,,
\end{equation}
so today (taking $\rho=\rho_m$ and $T=T_0$) the BAO-tuned choice implies
$\Delta s_{\rm cell,0}\approx 0.865\,\rho_{m,0}/T_0$, and the instantaneous creation power density is
$\sigma_0\simeq 2.595\,H_0\,\rho_{m,0}$ (the SI values are bookkeeping; the invariant target is $\sigma/(H\rho)$).

\section{Camouflage \& Detection}
\textbf{Invariant (dimensionless):} CMB acoustic angles, BAO ratios $D/r_d$, AP ratios, line ratios, $h\nu/k_BT$, $\omega/\omega_0$, normalized $a(k)$.
\textbf{Non-invariant (breaks camouflage):} $H_0$ in km/s/Mpc, $r_d$ in Mpc, $\sigma_8$ amplitude, Cavendish/lensing amplitudes, absolute temperatures and frequencies.

\section{Fill Independence}
The scaling $a(k)\propto k^{1/3}$ follows from locality, bounded degree, near-isotropy, and absence of persistent long-range order.
Specific fills (golden-angle, blue-noise, jittered lattice, RSA; inside-out vs.\ outside-in) share the same coarse volume law; we use golden-angle only as a reproducible generator in tests \cite{livio2002golden,jean1994phyllotaxis}.
Report diagnostics via two-point correlation/structure factor and a discrepancy score to certify the assumptions.

% --- Standard placeholders wired to external files if present ---
\clearpage
\IfFileExists{other_tex/acknowledgments.tex}{\input{other_tex/acknowledgments.tex}}{}
\IfFileExists{other_tex/funding.tex}{\input{other_tex/funding.tex}}{}
\IfFileExists{other_tex/authors_contributions.tex}{\input{other_tex/authors_contributions.tex}}{}
\IfFileExists{other_tex/competing_interests.tex}{\input{other_tex/competing_interests.tex}}{}
\IfFileExists{other_tex/data_accessibility.tex}{\input{other_tex/data_accessibility.tex}}{}
\IfFileExists{other_tex/disclosure.tex}{\input{other_tex/disclosure.tex}}{}

% ----------------
% Safe glossary (prints only if glossaries is loaded)
% ----------------
\IfGlossariesEnabled{
  %\clearpage
  \printglossary[title=Glossary]
}

% ----------------
% Bibliography (BibTeX by default)
% ----------------
\clearpage
\nocite{*} % avoid Empty thebibliography even with zero explicit \cite
\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}
