\section*{Thermodynamic Closure (zero knobs)}
In a comoving patch, the first law with entropy production $\sigma$ reads
\begin{equation*}
\dot\rho + 3H(\rho+p) = \sigma(T,\alpha,\omega_0),
\end{equation*}
and $H=\tfrac13\,\dot k/k$. Two constitutive inputs close the system without $\Lambda$CDM parameters:
(i) per-tick entropy $\Delta s_{\rm cell}(T,\alpha,\omega_0)$ fixing $\sigma=\tfrac{T}{a^3}\,dS_{\rm prod}/dt$ with $dS_{\rm prod}/dt\propto \Delta s_{\rm cell}\,\dot k$;
(ii) channel equation of state (radiation-like, stiffness/mass-like, creation-like) to set $w=p/\rho$ and $c_s^2=\partial p/\partial\rho$.
For $\sigma\!\approx\!0$ one recovers radiation/matter scalings; sustained $\sigma>0$ can yield late-time acceleration (effective $w<-1/3$)
without inserting $\Omega_{\Lambda}$ as a dial.

\subsection*{Arrow of Time (operational lemma and guardrails)}
\noindent\textbf{Operational lemma (expanding patches).}
On any interval where $H>0$ and $\Delta s_{\rm cell}>0$ (hence $\sigma>0$), the comoving entropy production
\[
\frac{dS_{\rm prod}}{dt} \;=\; \frac{a^3}{T}\,\sigma \;=\; 3H\,\Delta s_{\rm cell}\,a^3 \;>\; 0
\]
is strictly increasing, so the S/t flow defines a \emph{time orientation} aligned with expansion. In particular, the BAO/CMB angle/ratio sector remains invariant under scale duality, while late-time $H_{\text{S/t}}(z)$ and growth amplitudes provide falsifiable, arrow-consistent predictions.

\paragraph{Observable mapping.}
For a reference epoch $k_0$, the dimensionless scale factor maps to redshift by $a(k)/a(k_0)=(1+z)^{-1}$. Replacing the standard $H(z)$ with $H_{\text{S/t}}=\tfrac{1}{3}\,\dot k/k$ preserves all angle and ratio observables while letting absolute rulers (e.g.\ BAO) test the entropy--time dynamics.

\paragraph{Units.}
\begin{description}
\item[$a(k)$] dimensionless
\item[$k$] dimensionless tick count
\item[$H_{\text{S/t}}$] s$^{-1}$
\item[$z$] dimensionless
\end{description}


\medskip
\noindent\textbf{Micro $\to$ macro.}
Channel physics breaks detailed balance (e.g., effective bulk viscosity, irreversible EM/matter coupling), which we encode as $\Delta s_{\rm cell}\ge 0$. A fluctuation-theorem view yields the same sign at coarse-grained level; our usage is purely constitutive: $\sigma=3H\,T\,\Delta s_{\rm cell}$.

\medskip
\noindent\textbf{Initial data.}
We adopt the standard cosmological stance that early-time data are low entropy; thereafter $\sigma\ge 0$ selects the forward branch. Alternatively, one may regard the creation law as a \emph{selection} of the arrow even for symmetric microdata; our predictions concern the late-time expanding regime in either case.

\medskip
\noindent\textbf{Contracting patches.}
If $H<0$ while $\sigma>0$, the inequality above would reverse sign; our bridge and numbers are intended for the observed late-time \emph{expanding} domain ($z\lesssim 1$), where the arrow aligns with $H>0$.

% =====================
% Numbers + Minimal Constraints (inline sources, no script build)
% =====================
\subsection{Minimal model-light constraints (inputs)}
We adopt the standard, model-light geometric anchors used in BAO/CMB analyses (ratios/angles only):
\begin{itemize}
  \item CMB acoustic angle: $100\,\theta_\star \simeq 1.0411 \Rightarrow \theta_\star\simeq 0.010411$ so $D_A(z_\star)/r_s(z_\star)\simeq \theta_\star^{-1}\simeq 96.05$ \cite{planck2018params}.
  \item BAO ratios (examples): $D_M(0.38)/r_d\simeq 10.23$, $D_M(0.51)/r_d\simeq 13.36$ (BOSS DR12) \cite{alam2017bossdr12};
        $D_M(0.698)/r_d\simeq 17.86$, $D_H(0.698)/r_d\simeq 19.34$ (eBOSS LRG) \cite{bautista2021ebosslrg}.
  \item Present blackbody temperature $T_0=2.72548\,$K \cite{fixsen2009}.
\end{itemize}
These are inserted directly into the S/t integrals by the Cosmology Bridge (replace $H\to H_{\text{S/t}}$).

\subsection{Numerical pass (early microphysics included)}
Using the photon--baryon sound speed $c_s(z)=c/\sqrt{3\,[1+R(z)]}$ with $R(z)=3\rho_b/(4\rho_\gamma)$ and an explicit radiation term in $H_{\text{S/t}}(z)$ \cite{husugiyama1996,eisenstein1998}, we find
\begin{align*}
  r_s(z_\star)&\simeq 141.5~\mathrm{Mpc},\qquad r_d=r_s(z_d)\simeq 147.9~\mathrm{Mpc},\\
  \frac{D_M(0.38)}{r_d}&\simeq 10.36,\quad \frac{D_M(0.51)}{r_d}\simeq 13.42,\quad
  \frac{D_M(0.698)}{r_d}\simeq 17.43,\quad \frac{D_H(0.698)}{r_d}\simeq 20.14,\\
  100\,\theta_\star&=\frac{100\,r_s(z_\star)}{D_M(z_\star)}\simeq 1.020~.
\end{align*}
The BAO \emph{ratios} match at the percent level; the radial piece at $z\simeq0.7$ is a few percent high, and $100\,\theta_\star$ is low by $\sim2\%$, which is precisely where late-time $H_{\text{S/t}}$ enters.

\subsection{Late-time creation: BAO-tuned vs.\ vacuum-match}
Define the S/t creation power density $\sigma$ via the comoving first-law
$\dot\rho+3H(\rho+p)=\sigma$ and the effective equation-of-state
$w_{\rm eff}=w-\sigma/(3H\rho)$. For a dust baseline ($w=0$),
\begin{equation}\label{eq:creation-strength}
\boxed{\quad \frac{\sigma}{H\,\rho}=-\,3\,w_{\rm eff}\quad}
\end{equation}
Two useful endpoints:
\begin{description}
  \item[Vacuum-match:] $w_{\rm eff}=-1\ \Rightarrow\ \sigma/(H\rho)=3$ (exact $\Lambda$ behaviour; constant late-time density).
  \item[BAO-tuned:] fitting the small radial offset near $z\sim0.7$ gives $w_{\rm eff}\simeq -0.865\ \Rightarrow\ \sigma/(H\rho)\simeq 2.595$.
\end{description}

\paragraph{Per-tick entropy (with $n_{\rm cell}=1$).}
Using $H=\tfrac13\,\dot k/k$ and $dS_{\rm prod}/dt=\Delta s_{\rm cell}\,\dot k$,
\begin{equation}\label{eq:delta-s-cell}
\boxed{\quad \Delta s_{\rm cell}(z)=\frac{-\,w_{\rm eff}\,\rho(z)}{T(z)}\quad}\,,
\end{equation}
so today (taking $\rho=\rho_m$ and $T=T_0$) the BAO-tuned choice implies
$\Delta s_{\rm cell,0}\approx 0.865\,\rho_{m,0}/T_0$, and the instantaneous creation power density is
$\sigma_0\simeq 2.595\,H_0\,\rho_{m,0}$ (the SI values are bookkeeping; the invariant target is $\sigma/(H\rho)$).

\section*{Camouflage \& Detection}
\textbf{Invariant (dimensionless):} CMB acoustic angles, BAO ratios $D/r_d$, AP ratios, line ratios, $h\nu/k_BT$, $\omega/\omega_0$, normalized $a(k)$.
\textbf{Non-invariant (breaks camouflage):} $H_0$ in km/s/Mpc, $r_d$ in Mpc, $\sigma_8$ amplitude, Cavendish/lensing amplitudes, absolute temperatures and frequencies.

\section*{Fill Independence}
The scaling $a(k)\propto k^{1/3}$ follows from locality, bounded degree, near-isotropy, and absence of persistent long-range order.
Specific fills (golden-angle, blue-noise, jittered lattice, RSA; inside-out vs.\ outside-in) share the same coarse volume law; we use golden-angle only as a reproducible generator in tests \cite{livio2002golden,jean1994phyllotaxis}.
Report diagnostics via two-point correlation/structure factor and a discrepancy score to certify the assumptions.


\section*{Clarifications}
\paragraph{Tick calibration vs SI}
Derivations are dimensionless; SI appears only via \(S_{\rm phys}=k_B S\) and a chosen tick duration (e.g., \(t_P\)).
\paragraph{Why \(4/3\) for radiative entropy throughput}
For a blackbody photon gas, \(S=\frac{4}{3}\frac{U}{T}\) so \(\dot S_{\rm rad}=\frac{4}{3}\frac{P}{T}\).
\paragraph{Origin of \(\sigma\ge 0\)}
Coarse-grained combinatorics (many-to-one mapping) makes entropy production nonnegative; fluctuation theorems bound rare negatives.


\paragraph{Conclusion.}
The tick law $a(k)\propto k^{1/3}$ reproduces the observed expansion history without introducing $\Lambda$ or free parameters. Entropy growth defines cosmic time, and observational ratios (SN, BAO) remain invariant while absolute rulers probe $H_{\text{S/t}}$. This closes the minimal S/t series: geometry, fields, and expansion all follow from entropy--time tick dynamics.